---
title: "26R_code_chunks"
author: "nobuo"
date: "2021/3/22"
output: html_document
---
## 2.6 R code chunks and inline R code

```{r}
# execute code if the date is later than a specified day
do_it = Sys.Date() > '2018-02-14'
```


```{r, eval=do_it}
x = rnorm(100)
```

```{r, setup, include=FALSE}
knitr::opts_chunk$set(fig.width = 8, collapse = TRUE)
```

```{r}
x = 5  # radius of a circle
```

For a circle with the radius `r x`,
its area is `r pi * x^2`.

### 2.6.1 Figures

By default, figures produced by R code will be placed immediately after the code chunk they were generated from. For example:

```{r}
plot(cars, pch = 18)
```
```{r, fig.show='hold', out.width="50%"}
par(mar = c(4, 4, .2, .1))
plot(cars, pch = 19)
plot(pressure, pch = 17)
```

### 2.6.2 Tables

The easiest way to include tables is by using knitr::kable(), which can create tables for HTML, PDF and Word outputs.3 Table captions can be included by passing caption to the function, e.g.,

```{r tables-mtcars}
knitr::kable(iris[1:5, ], caption = 'A caption')
```